PineAPPL: EW and mixed QCD--EW corrections for PDF fits

### 2020-07-29 paper/sec-results.tex
Corrected values of the physical parameters

The values of the relevant physical parameters are chosen as
\begin{equation}
%\begin{aligned}
M_\mathrm{W} = \SI{80}{\giga\electronvolt} \text{,} \quad 
M_\mathrm{Z} = \SI{90}{\giga\electronvolt} \text{,} \quad 
m_\mathrm{t} = \SI{170}{\giga\electronvolt} \text{,} \quad
\Gamma_\mathrm{W} = \SI{2}{\giga\electronvolt} \text{,} \quad
\Gamma_\mathrm{Z} = \SI{2}{\giga\electronvolt} \text{,} 
\label{eq:parameters}
%\end{aligned}
\end{equation}
where $M_W$, $M_Z$ and $m_t$ are the values of the $W$-boson, $Z$-boson and
top quark masses, respectively, and $\Gamma_W$ and $\Gamma_Z$ are the width of
the $W$-boson and of the $Z$-boson, respectively. The value of the strong
coupling is chosen consistently with the PDF set, $\alpha_s(M_Z)=0.118$.

@@

Our goal is twofold. On the one hand, we aim to validate the fast interpolation
grids generated with {\sc PineAPPL}: to this purpose we shall verify that the
MC and the {\sc PineAPPL} results are identical up to numerical inaccuracies
due to the grid interpolation. This equivalence must hold for any choice of
renormalisation and factorisation scale. On the other hand, we aim to study
the size of the EW corrections, in particular with respect to the kinematics of
each process, and to an array of relative uncertainties coming from the PDFs,
the scale variations, and the experimental data.

>>>>

The values of the relevant physical parameters are chosen as
\begin{equation}
%\begin{aligned}
M_\mathrm{W} = \SI{80}{\giga\electronvolt} \text{,} \quad 
M_\mathrm{Z} = \SI{91.176}{\giga\electronvolt} \text{,} \quad 
m_\mathrm{t} = \SI{172.5}{\giga\electronvolt} \text{,} \quad
\Gamma_\mathrm{W} = \SI{2.50}{\giga\electronvolt} \text{,} \quad
\Gamma_\mathrm{Z} = \SI{2.09}{\giga\electronvolt} \text{,} 
\label{eq:parameters}
%\end{aligned}
\end{equation}
where $M_W$, $M_Z$ and $m_t$ are the values of the $W$-boson, $Z$-boson and
top quark masses, respectively, and $\Gamma_W$ and $\Gamma_Z$ are the width of
the $W$-boson and of the $Z$-boson, respectively. The value of the strong
coupling is chosen consistently with the PDF set, $\alpha_s(M_Z)=0.118$.

@@

Our goal is twofold. On the one hand, we aim to validate the fast interpolation
grids generated with {\sc PineAPPL}: to this purpose we shall verify that the
MC and the {\sc PineAPPL} results are identical up to numerical inaccuracies
due to the grid interpolation. This equivalence must hold for any choice of
renormalisation and factorisation scale. On the other hand, we aim to study
the size of the EW corrections, in particular with respect to the kinematics of
each process, and to an array of relative uncertainties arising from the PDFs,
the scale variations, and the experimental data.
